Expert-In-The-Loop Causal Discovery: Iterative Model Refinement Using Expert Knowledge

### 2024-11-27 paper/main.tex
Updates plot and makefile

\begin{figure}
	\centering
	\includegraphics[scale=0.4]{plots/web_tool_full.png}
	\caption{A screenshot of the web tool for constructing the model. Users
		can upload their dataset after which the tool creates an empty
		graph and shows all pair of variables which are associated in
		the model using undirected red edges with the strength of
		association represented using edge width. Users can then add
		edges to the model (shown in green). Unnecessary edges are shown in 
		black.}
\end{figure}

@@

\begin{figure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics{../code/plots/shd_ribbon.pdf}
		\caption{}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics{../code/plots/sid_ribbon.pdf}
		\caption{}
	\end{subfigure}
	\caption{Comparison of PC and Hill-Climb Search algorithms against
		manually drawn DAGs using the assistance method. As PC and
		Hill-Climb Search return the Markov Equivalence Class (MEC), we
		use the best and worst scoring orientation of the MEC to get
		the range of values. The human drawn values are done for
	multiple accuracy values of the oracle. \todo[inline]{Replace Hill-Climb with GES and improve the plot}}
\end{figure}

>>>>

% \begin{figure}
% 	\centering
% 	\includegraphics[scale=0.4]{plots/web_tool_full.png}
% 	\caption{A screenshot of the web tool for constructing the model. Users
% 		can upload their dataset after which the tool creates an empty
% 		graph and shows all pair of variables which are associated in
% 		the model using undirected red edges with the strength of
% 		association represented using edge width. Users can then add
% 		edges to the model (shown in green). Unnecessary edges are shown in 
% 		black.}
% \end{figure}

@@

\begin{figure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics{../code/fig3/shd_ribbon.pdf}
		\caption{}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics{../code/fig3/sid_ribbon.pdf}
		\caption{}
	\end{subfigure}
	\caption{Comparison of PC and Hill-Climb Search algorithms against
		manually drawn DAGs using the assistance method. As PC and
		Hill-Climb Search return the Markov Equivalence Class (MEC), we
		use the best and worst scoring orientation of the MEC to get
		the range of values. The human drawn values are done for
	multiple accuracy values of the oracle. \todo[inline]{Replace Hill-Climb with GES and improve the plot}}
\end{figure}
